Sparse Function Space Representation of Neural Networks for Exploration and Retention

### 2023-04-25 paper/main.tex
Minor additions

%\title{Investigatin Uncertainty Quantification in Model-based Reinforcement Learning}
% \title{Model-based Reinforcement Learning with Fast Posterior Updates}
%\title{Sequential Decision-Making under Uncertainty with Big Data}
% \title{Neural Network to Vatiational Sparse Gaussian Process: For Adaptive Exploration}
% \title{Neural Network to Sparse Variational Gaussian Process: For Updates in Sequential Decision Making}
% \title{Adapting Neural Networks to New Data For Updates in Sequential Decision Making via Gaussian Processes}
% \title{Converting Neural Networks to Gaussian Processes for Sequential Decision-Making Under Uncertainty}
\title{Sparse Function Space Representation of Neural Networks for Exploration and Representation}

@@

\begin{abstract}
Under sequential learning paradigms, such as Continual Learning (CL) or Reinforcement Learning (RL), deep learning training techniques show shortcomings in retaining previously acquired knowledge and adapting to evolving environments through exploration.
Retraining the model to incorporate new data or avoiding forgetting can be inefficient or impossible in many scenarios, setting hard constraints on time and hardware resources.
Existing techniques for converting trained neural networks from weight to function space allow a principled approach to the problem but still have scaling issues. In this paper, we present a method for sparsifying the representation of the neural networks in function space, which enables fast adaptation and compact representation that solves the limitations of the weight space formulation without the well-known flaws associated with nonparametric models.
\end{abstract}

\section{Introduction}
\label{sec:intro}
%
Neural networks have experienced unparalleled success in the large data, offline and gradient-based training regime. 
Deep learning is great and in the suerpvised and unsupervised setting solve large-scale problems.
How about sequential learning problems such as continual or reinforcement learning.
In continual learning mainitaining a compact representation

>>>>

%\title{Investigatin Uncertainty Quantification in Model-based Reinforcement Learning}
% \title{Model-based Reinforcement Learning with Fast Posterior Updates}
%\title{Sequential Decision-Making under Uncertainty with Big Data}
% \title{Neural Network to Vatiational Sparse Gaussian Process: For Adaptive Exploration}
% \title{Neural Network to Sparse Variational Gaussian Process: For Updates in Sequential Decision Making}
% \title{Adapting Neural Networks to New Data For Updates in Sequential Decision Making via Gaussian Processes}
% \title{Converting Neural Networks to Gaussian Processes for Sequential Decision-Making Under Uncertainty}
\title{Sparse Function Space Representation of Neural Networks for Exploration and Retention}

@@

\begin{abstract}
Under sequential learning paradigms, such as Continual Learning or Reinforcement Learning, deep learning training techniques show shortcomings in retaining previously acquired knowledge and adapting to evolving environments through exploration.
Retraining the model to incorporate new data or avoiding forgetting can be inefficient or impossible in many scenarios, setting hard constraints on time and hardware resources.
Existing techniques for converting trained neural networks from weight to function space allow a principled approach to the problem but still have scaling issues. In this paper, we present a method for sparsifying the representation of the neural networks in function space, which enables fast adaptation and compact representation that solves the limitations of the weight space formulation without the well-known flaws associated with nonparametric models.\looseness-1
\end{abstract}

\section{Introduction}
\label{sec:intro}
%
%Neural networks have experienced unparalleled success in the large data, offline and gradient-based training regime. Deep learning is great and in the suerpvised and unsupervised setting solve large-scale problems.
%How about sequential learning problems such as continual or reinforcement learning. In continual learning mainitaining a compact representation
Deep learning has experienced unparalleled success in contemporary artificial intelligence (AI), contributing to advancements in various domains ranging from computer vision to natural language processing. The capacity of deep learning models to process and learn complex patterns from large-scale supervised and unsupervised learning tasks has led to impressive breakthroughs in applications in the large data, offline, and gradient-based training regime. Despite this remarkable success, several challenges remain when employing gradient-based learning techniques in sequential learning paradigms such as continual learning and reinforcement learning.
